---
title: "Unit 6 LIve Session R Code"
output: html_document
editor_options: 
  chunk_output_type: console
---

$ Unit 6 Question 1
Loading, Splitting in Training / Test, Classifying, Evaulating the Model
```{r}
library(caret)

titanicDataDF = read.csv("https://raw.githubusercontent.com/BivinSadler/MSDS_6306_Doing-Data-Science/Master/Unit%206/titanic_train.csv",header = TRUE)

head(titanicDataDF)

titanicDataDF$SurvivedF = factor(titanicDataDF$Survived, labels = c("Died", "Survived"))

head(titanicDataDF)

trainIndex = sample(seq(1,891,1),600)
trainTitanic = titanicDataDF[trainIndex,]
testTitanic = titanicDataDF[-trainIndex,]

dim(trainTitanic)
dim(testTitanic)

#Plot
trainTitanic %>% ggplot(aes(x = Pclass, y = Age, col = SurvivedF)) + geom_point() + ggtitle("Survival v. Age and Passenger Class") + xlab("Passenger Class")  + 
  geom_jitter()

# We will assume that the ages are missing at random.
trainTitanic= na.omit(trainTitanic)
testTitanic = na.omit(testTitanic)

dim(trainTitanic)
dim(testTitanic)

classifications = knn(train = trainTitanic[(!is.na(trainTitanic$Age) & !is.na(trainTitanic$Pclass)),c("Pclass","Age")], test = testTitanic[(!is.na(testTitanic$Age) & !is.na(testTitanic$Pclass)),c(3,6)], cl = trainTitanic$Survived[(!is.na(trainTitanic$Age) & !is.na(trainTitanic$Pclass))], prob = TRUE, k = 5)

table(classifications,testTitanic$Survived[(!is.na(testTitanic$Age) & !is.na(testTitanic$Pclass))])
CM = confusionMatrix(table(classifications,testTitanic$Survived[(!is.na(testTitanic$Age) & !is.na(testTitanic$Pclass))]))
CM

CM = confusionMatrix(table(classifications,testTitanic$Survived[(!is.na(testTitanic$Age) & !is.na(testTitanic$Pclass))]),mode = "everything")
CM
```

## Internal LOOCV
```{r}
# Using just the training data
classifications = knn.cv(trainTitanic[,c("Age","Pclass")], trainTitanic$SurvivedF,k = 5)

CM = confusionMatrix(table(classifications,trainTitanic$SurvivedF[(!is.na(trainTitanic$Age) & !is.na(trainTitanic$Pclass))]),mode = "everything")
CM

# Using all the data
titanicDataDF_NO_NA = na.omit(titanicDataDF)

classifications = knn.cv(titanicDataDF_NO_NA[,c("Age","Pclass")], titanicDataDF_NO_NA$SurvivedF,k = 5)

CM = confusionMatrix(table(classifications,titanicDataDF_NO_NA$SurvivedF[(!is.na(titanicDataDF_NO_NA$Age) & !is.na(titanicDataDF_NO_NA$Pclass))]),mode = "everything")
CM


```



Predicting Survial for a 30 year old in 1st,2nd,3rd class
```{r}
Thirty1= data.frame(Age = 30, Pclass = 1)
Thirty2= data.frame(Age = 30, Pclass = 2)
Thirty3= data.frame(Age = 30, Pclass = 3)

knn(titanicDataDF[(!is.na(titanicDataDF$Age) & !is.na(titanicDataDF$Pclass)),c(3,6)],Thirty1,titanicDataDF$Survived[(!is.na(titanicDataDF$Age) & !is.na(titanicDataDF$Pclass))], prob = TRUE, k = 5)

knn(titanicDataDF[(!is.na(titanicDataDF$Age) & !is.na(titanicDataDF$Pclass)),c(3,6)],Thirty2,titanicDataDF$Survived[(!is.na(titanicDataDF$Age) & !is.na(titanicDataDF$Pclass))], prob = TRUE, k = 5)

knn(titanicDataDF[(!is.na(titanicDataDF$Age) & !is.na(titanicDataDF$Pclass)),c(3,6)],Thirty3,titanicDataDF$Survived[(!is.na(titanicDataDF$Age) & !is.na(titanicDataDF$Pclass))], prob = TRUE, k = 5)

```

Classify the 418 from the other test set.  We don't have the true labels for these... you can get a score for these by submitting them to Kaggle. (where I got the test set from.)
```{r}

testTitanicKaggle = read.csv(file.choose(),header = TRUE)
names(testTitanicKaggle)[2] = "Pclass"
names(testTitanicKaggle)[5] = "Age"

testTitanicKaggleClean = testTitanicKaggle[(!is.na(testTitanicKaggle$pclass) & !is.na(testTitanicKaggle$age)),]

classifications = knn(trainTitanic[(!is.na(trainTitanic$age) & !is.na(trainTitanic$pclass)),c(4,6)],testTitanicKaggleClean[,c(5,2)],trainTitanic$survived[(!is.na(trainTitanic$age) & !is.na(trainTitanic$pclass))], prob = TRUE, k = 5)

```

# Adding in Male and Female: Categorical Variables
```{r}
library(tidyverse)

#Male
trainTitanicMale = trainTitanic %>% filter(Sex == "male")
testTitanicMale = testTitanic %>% filter(Sex == "male")

classificationsMale = knn(trainTitanicMale[(!is.na(trainTitanicMale$Age) & !is.na(trainTitanicMale$Pclass)),c(3,6)],testTitanicMale[(!is.na(testTitanicMale$Age) & !is.na(testTitanicMale$Pclass)),c(3,6)],trainTitanicMale$Survived[(!is.na(trainTitanicMale$Age) & !is.na(trainTitanicMale$Pclass))], prob = TRUE, k = 55)

#Female
trainTitanicFemale = trainTitanic %>% filter(Sex == "female")
testTitanicFemale = testTitanic %>% filter(Sex == "female")

classificationsFemale = knn(trainTitanicFemale[(!is.na(trainTitanicFemale$Age) & !is.na(trainTitanicFemale$Pclass)),c(3,6)],testTitanicFemale[(!is.na(testTitanicFemale$Age) & !is.na(testTitanicFemale$Pclass)),c(3,6)],trainTitanicFemale$Survived[(!is.na(trainTitanicFemale$Age) & !is.na(trainTitanicFemale$Pclass))], prob = TRUE, k = 55)

classificationsMF = factor(c(classificationsMale,classificationsFemale), labels = c("No","Yes"))

testM = testTitanicMale[(!is.na(testTitanicMale$Age) & !is.na(testTitanicMale$Pclass)),]
testF = testTitanicFemale[(!is.na(testTitanicFemale$Age) & !is.na(testTitanicFemale$Pclass)),]

testMF = rbind(testM,testF)

table(classificationsMF,testMF$Survived[(!is.na(testMF$Age) & !is.na(testMF$Pclass))])
CM = confusionMatrix(table(classificationsMF,factor(testMF$Survived[(!is.na(testMF$Age) & !is.na(testMF$Pclass))], labels = c("No", "Yes"))), mode = "everything")
CM
```



# Question 2

```{r}
set.seed(1)
iterations = 5
numks = 10
splitPerc = .8

masterAcc = matrix(nrow = iterations, ncol = numks)

for(j in 1:iterations)
{
  trainIndices = sample(1:dim(iris)[1],round(splitPerc * dim(iris)[1]))
  train = iris[trainIndices,]
  test = iris[-trainIndices,]
  for(i in 1:numks)
  {
    classifications = knn(train[,c(1,3)],test[,c(1,3)],train$Species, prob = TRUE, k = i)
    table(classifications,test$Species)
    CM = confusionMatrix(table(classifications,test$Species))
    masterAcc[j,i] = CM$overall[1]
  }
  
}

MeanAcc = colMeans(masterAcc)

plot(seq(1,numks,1),MeanAcc, type = "l")

which.max(MeanAcc)
max(MeanAcc)

```

# BONUS
```{r}
set.seed(1)
iterations = 10
numks = 20

masterAcc = matrix(nrow = iterations, ncol = numks)

for(j in 1:iterations)
{
  
  for(i in 1:numks)
  {
    CM = confusionMatrix(table(iris[,5],knn.cv(iris[,c(1,2)],iris[,5],k = i)))
    masterAcc[j,i] = CM$overall[1]
    
  }
  
}

MeanAcc = colMeans(masterAcc)

plot(seq(1,numks,1),MeanAcc, type = "l")

which.max(MeanAcc)
max(MeanAcc)
```