---
title: "Unit 5 For Live Session Solution"
author: "Bivin"
date: "9/23/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---


# Unit 5 Live Session R Code

## Part 1 BBall

Creating the TotalInches column:
```{r}
BBall = read.csv(file.choose(),header = TRUE)
head(BBall)
BBall = BBall %>% separate(height, c("feet","inches"), remove = FALSE) %>% mutate(TotalInches = 12*as.numeric(feet) + as.numeric(inches))

BBall[2143,]
#https://en.wikipedia.org/wiki/George_Karl
BBall[2143,"height"] = "6-10"
BBall[2143,"weight"] = "185"
BBall[2143,"TotalInches"] = 6*12 + 10

#Check our cleaning
BBall[2143,]

head(BBall)
class(BBall$TotalInches)
class(BBall$weight)
BBall$weight = as.numeric(BBall$weight)
class(BBall$weight)

```

Making the histogram:
```{r}
BBall %>% ggplot(aes(x = TotalInches, color = position)) + geom_histogram() + facet_wrap(~position)
```

# Breakout: Create a column plot the compares the average height of all players that have come from Duke University, SMU and Texas Tech University.  
```{r}

```

## Part 2 Soccer (Football)

Creating the To
```{r}
FIFA = read.csv(file.choose(),header = TRUE)

head(FIFA)

FIFA = FIFA %>% separate(Height, c("feet","inches"),sep = "'", remove = FALSE) %>% mutate(TotalInches = 12*as.numeric(feet) + as.numeric(inches)) %>% mutate(WeightNum = as.numeric(str_sub(FIFA$Weight,1,3)))
head(FIFA)

#Another way for weight:
FIFA = FIFA %>% separate(Height, c("feet","inches"),sep = "'", remove = FALSE) %>% mutate(TotalInches = 12*as.numeric(feet) + as.numeric(inches)) %>% mutate(WeightNum2 = as.numeric(str_replace(FIFA$Weight, "lbs", "")))
head(FIFA)

#or 

FIFA = FIFA %>% separate(Height, c("feet","inches"), sep = "'", remove = FALSE) %>% mutate(TotalInches = 12*as.numeric(feet) + as.numeric(inches)) %>% mutate(WeightNum3 = as.numeric(str_replace(FIFA$Weight, "...$", "")))
head(FIFA)

```

There appears to be a strong positive and linear relationship beween height and weigth (as you would expect).  But is it the same for positions LM and LB?
```{r}
FIFA %>% ggplot(aes(x = WeightNum, y = TotalInches)) + geom_point() + ggtitle("Height v. Weight")
```

Visually, there is not a lot of evidence to suggest the  relationship is different. 
```{r}
FIFA %>% filter(Position == "LB" | Position == "LM") %>% ggplot(aes(x = WeightNum, y = TotalInches, color = Position)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Height v. Weight (LM vs. LB)") +facet_wrap(~Position) + xlab("Weight (lbs)") + ylab("Height (inches)")

```

## Break Out FIFA
Assess a potential relationship between Wage v. Value (hint: use if_else() in your solution)
```{r}


```


## Part 3: Baby Names

```{r}
# 1A
# setwd()
df <- read.table(file.choose(), sep=";", header=FALSE, col.names = c("Name", "Gender", "BornThisYear"))
head(df)

#df$Gender = factor(df$Gender)

# 1B
summary(df)
str(df)

#1C
df$Name[grep("y{3}", df$Name)] # There are others, of course; this regular expression does not even say it's at the end of the word

#1D 
y2016 <- df[-grep("y{3}", df$Name),] # You could also hard-code which row it is, but I recommend this.

# 2A
y2015 <- read.table(file.choose(), sep=",", header=FALSE, col.names = c("Name", "Gender", "BornThisYear"))
head(y2015, n = 2000)
# Notice that my columns are the same name.  If students have different names, the code below changes a little.


#2B
tail(y2015,n=2000)
# For 'interesting,' it could be a lot of things.  For one, all 10 are male.  All 10 start with the letter Z.  All are unpopular names. The data set is ordered by gender and then by BornThisYear and then alphabetically by Name.  

#Let's order the list only by Born this year agnostic to gender.
y2015 %>% arrange(desc(BornThisYear))

#2C
final<-merge(y2016, y2015, by=c("Name", "Gender"), all=FALSE) # There are other combinations of this.  Inner Join
head(final)

#3A
final$Total <- final$BornThisYear.x + final$BornThisYear.y # Creating column
head(final)
sum(final$Total) # Figuring out everyone in it

#3B
a<-data.frame(final[order(-final$Total), c("Name", "Gender","Total")]) 
# You could also do tail here if you did ascending order.
head(a, n=10)

b<- final %>% arrange(desc(Total))
head(b, n=10)


#3C
# Lots of strategies here.  You could include only girls, omit only boys, use group bys, etc.  Use your judgment as grader.
girl<-head(a[a$Gender!="M",], n=10)
# It doesn't have to be as elegant a solution as this.  I just care that they get around here.
head(girl)
girl

girl2 = head(b %>% filter(Gender == "F"), n = 10)
head(girl2)
girl2

# 3D
girl<-girl[,c("Name", "Total")]
girl2 = girl2 %>% select(Name,Total)
head(girl)
head(girl2)

write.csv(girl2, "itsagirl.csv", row.names = FALSE)


# 4 Visualization

#girl$Name = droplevels(girl$Name)

girl %>% ggplot(aes(x = factor(Name, levels = Name[order(Total)]), y = Total, color = Name)) + geom_col() + ggtitle("Top 10 Girl Names!") + theme(legend.position = "none") + xlab("Name")

boy<-head(a[a$Gender == "M",], n=10)
boy2 = head(b %>% filter(Gender == "M"))

#boy$Name = droplevels(boy$Name)

boy %>% ggplot(aes(x = factor(Name, levels = Name[order(Total)]), y = Total, col = Name)) + geom_col() + ggtitle("Top 10 Boy Names!") + theme(legend.position = "none") + xlab("Name")

```
